---
title: "My reproducible science project"
author: 
  - 'Virginia Barley'
  - 'Virginia Tech, School of Plant and Environmental Science'
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    df_print: paged
  pdf_document: default
header-includes:
- \usepackage{amsmath}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Abstract

Barley is awesome!

## Introduction 

Something about QTL for grain yield and powdery mildew being described here and there.

## Materials and Methods

Blah blah blah... some number of genotypes were planted in the fall of 2021, and scored for powdery mildew in the spring of 2022...

Here is where I am going to clean the data 
```{r}
source("cleanDataExample.R")
```

This is where I conducted the analysis 
```{r}
source("dataAnalysis.R")
```


## Results

Here I will print some plots
```{r}
manhattan(resultList[[1]], main = traits[1])
manhattan(resultList[[2]], main = traits[2])
```


## Discussion

QTL for grain yield are the same as QTL for powdery mildew, suggesting yield is simply a function of how sick you got.